\documentclass[11pt]{article}
\usepackage[a4paper, margin=0.5in, showframe=false]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{mathptmx}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage[super]{nth}
\renewcommand{\labelitemi}{\textbullet}
\usepackage{enumitem}
\usepackage{fontawesome}


\thispagestyle{empty}
\definecolor{myBlue}{rgb}{.2, .35, .59}
\definecolor{darkBlue}{rgb}{.094117, .2, .3529}
\hypersetup{
  colorlinks   = true,      % Color links instead of boxes
  urlcolor     = myBlue, % Color for external hyperlinks
  linkcolor    = darkBlue,  % Color of internal links
  citecolor    = red        % Color of citations
}

\begin{document}

  \centerline{\Large{Alejandra J. Perea Rojas}}\vspace{1mm}

  \centerline{
    \href{mailto:aperearojas@college.harvard.edu}{\faEnvelopeO~aperearojas@college.harvard.edu} 
    $\cdot$ \href{https://github.com/alejandraprj}{\faGithub~github.com/alejandraprj}
    $\cdot$ \href{https://alejandraprj.com}{\faGlobe~alejandraprj.com}
  }\vspace{2mm}

  % Education
  \noindent{\textsc{\large Education}}\vspace{-7pt}\\
  \noindent\makebox[\linewidth]{\rule{7.5in}{0.3pt}}

  \noindent \textbf{Harvard University} \hfill Cambridge, MA
    \begin{itemize}[itemsep=-.4em, leftmargin=1em]\vspace{-2mm}
        \item Bachelor of Arts in Computer Science; Secondary in Physics. \hfill Anticipated: May 2024
        \item Relevant coursework: 
          Algorithms, 
          Systems Programming and Machine Organization,
          Abstraction and Design in Computation, 
          Applied Linear Algebra, Probability,
          Electromagnetism, Mechanics, 
          and Artificial Intelligence.
    \end{itemize}
        % Quantum Mechanics % General Data Structures and Algorithms % Wave Phenomena 

  % Relevant Experience
  \noindent{\textsc{\large Experience}}\vspace{-7pt}\\
  \noindent\makebox[\linewidth]{\rule{7.5in}{0.3pt}}

    % PAWS
    \noindent \textbf{Software Engineer}\\
    \textsc{{Teamcore at Harvard University}} \hfill Jun-Dec 2022, Cambridge, MA
    \begin{itemize}[itemsep=-.4em, leftmargin=1em]\vspace{-2mm}
      \item Revamped error handling for the PAWS SMART API by programming an interface that expedited testing requests. 
      \item Worked with QGIS to craft a set of artificial data used to verify predictions of poaching trap locations.
      \item Developed the interface with Python to handle requests in JSON form and wrote a document to detail procedures.
    \end{itemize}
    
    % WCS
    \noindent \textbf{Sensors Intern}\\
    \textsc{{Wildlife Conservation Society}} \hfill May-Aug 2022, Remote / NY
    \begin{itemize}[itemsep=-.4em, leftmargin=1em]\vspace{-2mm}
      \item Built three article processing programs with Python and initiated a large set of SQL queries to help develop a database.
      \item Researched and drafted a 
      \href{https://bit.ly/AI-Advancing-Video-Processing-and-CTDS}{white-paper} to review state-of-the-art AI video processing and conservation-related tools.
    \end{itemize}

    \noindent \textbf{AI Intern}\\
    \textsc{{C Minds through DRCLAS}} \hfill Apr-Aug 2021, Remote / MX
    \begin{itemize}[itemsep=-.4em, leftmargin=1em]\vspace{-2mm}
      \item Interned at a women-led action tank for ethical AI through the David Rockefeller Center for Latin American Studies.
      \item Helped install an AI Living Lab in Yucatan and establish a Diabetic Retinopathy AI Screening Program in Jalisco.
    \end{itemize}

  % Activities
  \noindent{\textsc{\large Activities}}\vspace{-7pt}\\
  \noindent\makebox[\linewidth]{\rule{7.5in}{0.3pt}}

  % WEB DIRECTOR OF HPC!

  % CS61
  \noindent\textbf{Systems Course Assistant}  \\
  \textsc{COMPSCI 61 at Harvard SEAS} \hfill Sep-Dec 2022, Cambridge, MA
  \begin{itemize}[itemsep=-.4em, leftmargin=1em]\vspace{-2mm}
    \item Facilitated a college class of about 200 students by holding office hours and a section of about 25 students weekly.
    \item Covered data memory and representation, assembly, kernel, caching, shell, and process synchronization using C++.
  \end{itemize}

  % WiCS
  \noindent\textbf{DIB Advocacy Director} \\
  \textsc{Women in Computer Science} \hfill Aug-Dec 2022, Cambridge, MA
  \begin{itemize}[itemsep=-.4em, leftmargin=1em]\vspace{-2mm}
    \item Oversaw and collabaroateed with 8 members on initiatives to promote diversity and inclusion. Organized events to provide more resources to underrepresented groups.
  \end{itemize}

  % Projects
  \noindent{\textsc{\large Projects}}\vspace{-7pt}\\
  \noindent\makebox[\linewidth]{\rule{7.5in}{0.3pt}}

    % CS182
    \noindent \textbf{COMPSCI 182} - \href{http://procaccia.info/courses/CS182-F22/pset2.pdf}{\textsc{Sudoku Solver}} and \href{http://procaccia.info/courses/CS182-F22/pset3.pdf}{\textsc{Ghost AI}} \hfill Oct-Dec 2022
    \begin{itemize}[itemsep=-.4em, leftmargin=1em]\vspace{-2mm}
      \item Created a Sudoku Solver using forward checking and MRV heuristics as a computer satisfaction problem.
      \item Developed a Ghost AI with Minimax Agents and Alpha Beta Agents with alpha-beta pruning. 
    \end{itemize}\vspace{-1mm}

    % MiniML CS51 % it's obvious that it's turing complete
    \noindent \textbf{COMPSCI 51} - \href{https://book.cs51.io/pdfs/abstraction-21-project.pdf}{\textsc{MiniML}} \hfill May 2022
    \begin{itemize}[itemsep=-.4em, leftmargin=1em]\vspace{-2mm}
      \item Built an OCaml interpreter with various features, including unary and binary types, operators, conditionals, and higher-order and recursive functions, using the substitution and dynamic scoped environment models. 
    \end{itemize}\vspace{-1mm}

    % CS61
    \noindent \textbf{COMPSCI 61} - 
      \href{https://cs61.seas.harvard.edu/site/2021/WeensyOS/}{\textsc{Kernel}} and 
      \href{https://cs61.seas.harvard.edu/site/2021/Shell/}{\textsc{Shell}} \hfill Oct-Dec 2021
    \begin{itemize}[itemsep=-.4em, leftmargin=1em]\vspace{-2mm}
      \item Implemented a kernel, called WeensyOS, with features such as kernel isolation, process isolation, virtual page allocation, forking, shared memory, and overlapping virtual memory address spaces, as well as an exiting function.
      \item Created a Bash shell in C++ with foreground and background commands (including the cd command), command lists, conditionals, pipelines, redirections, and the interrupt signal, while handling zombie processes.
    \end{itemize}

   % Skills
   \noindent{\textsc{\large Skills}}\vspace{-7pt}\\
   \noindent\makebox[\linewidth]{\rule{7.5in}{0.3pt}}
   \begin{itemize}[itemsep=-.4em, leftmargin=1em]\vspace{-2mm} % okk Go.. 
     \item \textbf{Programming:} Proficient (3+ years) in Python and C++. Experienced (1+ years) with Go, OCaml, Java, and SQL.
     \item \textbf{Development:} Proficient (3+ years) in HTML/CSS. Experienced (1+ years) with PHP, JavaScript, React, and Flask.
     % \noindent \textbf{Deployed:}  
     %   \href{https://alejandraprj.com}{www.alejandraprj.com},
     %   \href{https://harvardpsychedelicsclub.org}{www.harvardpsyschedelicsclub.org}\\
     \item \textbf{Environments:} Skilled with Linux, x86 Assembly, Azure, AWS, Docker, and MATLAB.
     \item \textbf{Language:} 
       Fluent in Spanish (native), intermediate in Mandarin Chinese, and elementary in Japanese.
   \end{itemize}


\end{document} 

