\documentclass[11pt]{article}
\usepackage[letterpaper, margin=0.5in, showframe=false]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{mathptmx}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage[super]{nth}
\renewcommand{\labelitemi}{\textbullet}
\usepackage{enumitem}
\usepackage{fontawesome}


\thispagestyle{empty}
\definecolor{myBlue}{rgb}{.2, .35, .59}
\definecolor{darkBlue}{rgb}{.094117, .2, .3529}
\hypersetup{
  colorlinks   = true,      % Color links instead of boxes
  urlcolor     = myBlue, % Color for external hyperlinks
  linkcolor    = darkBlue,  % Color of internal links
  citecolor    = red        % Color of citations
}

\begin{document}

  \centerline{\Large{Alejandra J. Perea Rojas}}\vspace{1mm}

  \centerline{
    \href{mailto:aperearojas@college.harvard.edu}{\faEnvelopeO~aperearojas@college.harvard.edu} 
    $\cdot$ \href{https://github.com/alejandraprj}{\faGithub~github.com/alejandraprj}
    $\cdot$ \href{https://alejandraprj.com}{\faGlobe~alejandraprj.com}
  }\vspace{2mm}

  % Education
  \noindent{\textsc{\large Education}}\vspace{-7pt}\\
  \noindent\makebox[\linewidth]{\rule{7.5in}{0.3pt}}

  \noindent \textbf{Harvard University} \hfill Cambridge, MA
    \begin{itemize}[itemsep=-.4em, leftmargin=1em]\vspace{-2mm}
        \item Bachelor of Arts in Computer Science; Secondary in Physics. \hfill Anticipated: May 2024
        \item Relevant coursework: 
          Algorithms, 
          Systems Programming and Machine Organization,
          Abstraction and Design in Computation, 
          Applied Linear Algebra, Probability,
          Electromagnetism, Mechanics, 
          and Artificial Intelligence.
    \end{itemize}
        % Quantum Mechanics % General Data Structures and Algorithms % Wave Phenomena 

  % Teaching
  \noindent\textsc{\large Teaching Experience}\vspace{-7pt}\\
  \noindent\makebox[\linewidth]{\rule{7.5in}{0.3pt}}
   
   \noindent\textbf{Course Assistant} \\
   \textsc{Harvard SEAS} \hfill Sep-Dec 2022, Cambridge, MA
   \begin{itemize}[itemsep=-.4em, leftmargin=1em]\vspace{-2mm}
     \item Facilitated COMPSCI 61, college-level course of about 200 students, by holding office hours and review sections weekly.
     \item Covered data memory and representation, assembly, kernel, caching, shell, and process synchronization using C++.
   \end{itemize}\vspace{-1mm}
   \textsc{Fox Lane Middle School} \hfill Apr-Jun 2019, Bedford, NY
   \begin{itemize}[itemsep=-.4em, leftmargin=1em]\vspace{-2mm}
     \item Full-time teacher assistant for Algebra 1 in two classes and 6th-grade Math in another class. 
     \item Assisted students in class, with homework, and helped grade exams and assignments.
   \end{itemize}

   \noindent\textbf{Tutor} \\
   \textsc{Independent Tutoring} \hfill Jun 2018-Present, NY / MA
   \begin{itemize}[itemsep=-.4em, leftmargin=1em]\vspace{-2mm}
    \item One-on-one tutoring in AP Physics, AP Chemistry, AP Computer Science, AP Calculus BC, Algebra, and Geometry.
   \end{itemize}\vspace{-1mm}
   \textsc{Incognity Academy}\hfill Jun-Aug 2021, Remote / Peru
   \begin{itemize}[itemsep=-.4em, leftmargin=1em]\vspace{-2mm}
     \item Developed a summer SAT prep and a mentorship program for students in Peru aiming to study in the United States. 
     \item Held review sessions twice weekly and led the English section of the SAT.
   \end{itemize}\vspace{-1mm}
   \textsc{Puente Tutoring} \hfill Sep 2017-Jun 2019, Bedford, NY
   \begin{itemize}[itemsep=-.4em, leftmargin=1em]\vspace{-2mm}
     \item Tutoring and mentoring middle school students in the English as a Second Language program with Algebra and English.
     \item As president of the club Puente, recruited tutoring volunteers, increasing the club's volume from 2 to 36.
   \end{itemize}

   \noindent\textbf{Speaker and Mentor}\\
   \textsc{Harvard Allston Education Portal} \hfill Jun-Aug 2020, Cambridge, MA
   \begin{itemize}[itemsep=-.4em, leftmargin=1em]\vspace{-2mm}
     \item Designed and led ELA classes for 6-8th graders for a remote summer class. Lessons held daily for three hours a day.
     \item Participated as a speaker in summer sessions on Zoom and guided students on their transition to high school.
   \end{itemize} 

   % Relevant Experience
  \noindent{\textsc{\large Engineering Experience}}\vspace{-7pt}\\
  \noindent\makebox[\linewidth]{\rule{7.5in}{0.3pt}}

    % PAWS
    \noindent \textbf{Software Engineer}\\
    \textsc{{TeamCore PAWS}} \hfill Jun-Dec 2022, Cambridge, MA
    \begin{itemize}[itemsep=-.4em, leftmargin=1em]\vspace{-2mm}
      \item Improved error handling for the \href{https://github.com/lily-x/paws-smart-api}{PAWS SMART API} by programming an interface and framework that expedited the API's local deployment and set-up. Also worked with QGIS to craft in Python the large set of artificial data used for testing.
      \item Developed the interface with Python to handle a suite of requests in JSON form and wrote a document to detail procedures.
    \end{itemize}
    
    % WCS
    \noindent \textbf{Drones and Sensors Intern}\\
    \textsc{{Wildlife Conservation Society}} \hfill May-Aug 2022, Remote / NY
    \begin{itemize}[itemsep=-.4em, leftmargin=1em]\vspace{-2mm}
      \item Built an article processing program with Python and crafted a set of SQL queries to help develop an online database.
      \item Researched and drafted a 
      \href{https://bit.ly/AI-Advancing-Video-Processing-and-CTDS}{white-paper} to review state-of-the-art AI-based video processing and conservation-related tools.
    \end{itemize}

    \noindent \textbf{AI Intern}\\
    \textsc{{C Minds through DRCLAS}} \hfill Apr-Aug 2021, Remote / MX
    \begin{itemize}[itemsep=-.4em, leftmargin=1em]\vspace{-2mm}
      \item Interned at a women-led action tank for ethical AI through the David Rockefeller Center for Latin American Studies.
      \item Helped install an AI Living Lab in Yucatan and establish a Diabetic Retinopathy AI-based Screening Program in Jalisco. 
    \end{itemize}

   % Skills
   \noindent{\textsc{\large Skills}}\vspace{-7pt}\\
   \noindent\makebox[\linewidth]{\rule{7.5in}{0.3pt}}
   \begin{itemize}[itemsep=-.4em, leftmargin=1em]\vspace{-2mm}
     \item \textbf{Programming:} Proficient (3+ years) in Python and C++. Experienced (1+ years) with OCaml, Java, and SQL.
     \item \textbf{Development:} Proficient (3+ years) in HTML/CSS. Experienced (1+ years) with PHP, JavaScript, React, and Flask.
     % \noindent \textbf{Deployed:}  
     %   \href{https://alejandraprj.com}{www.alejandraprj.com},
     %   \href{https://harvardpsychedelicsclub.org}{www.harvardpsyschedelicsclub.org}\\
     \item \textbf{Environments:} Skilled with Azure, AWS, Docker, and MATLAB.
     \item \textbf{Language:} 
       Fluent in Spanish (native), intermediate in Mandarin Chinese, and elementary in Japanese.
   \end{itemize}

   
\end{document} 
