\documentclass[11pt]{article}
\usepackage[letterpaper, margin=0.5in, showframe=false]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{mathptmx}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage[super]{nth}
\renewcommand{\labelitemi}{\textbullet}
\usepackage{enumitem}
\usepackage{fontawesome5}


\thispagestyle{empty}
\definecolor{myBlue}{rgb}{.2, .35, .59}
\definecolor{darkBlue}{rgb}{.094117, .2, .3529}
\hypersetup{
  colorlinks   = true,      % Color links instead of boxes
  urlcolor     = darkBlue, % Color for external hyperlinks
  linkcolor    = myBlue,  % Color of internal links
  citecolor    = red        % Color of citations
}

\begin{document}

  \centerline{\Large{Alejandra J. Perea Rojas}}\vspace{1mm}

  \centerline{
    \href{mailto:aperearojas@college.harvard.edu}{\color{darkBlue}\faEnvelope~aperearojas@college.harvard.edu} 
    $\cdot$ \href{https://github.com/alejandraprj}{\color{darkBlue}\faGithub~github.com/alejandraprj}
    $\cdot$ \href{https://alejandraprj.com}{\color{darkBlue}\faGlobe~alejandraprj.com}
  }\vspace{2.5mm}

  % Education
  \noindent{\textsc{\large Education}}\vspace{-8pt}\\
  \noindent\makebox[\linewidth]{\rule{7.5in}{0.3pt}}

  \noindent \textbf{Harvard University} \hfill Cambridge, MA
    \begin{itemize}[itemsep=-.4em, leftmargin=1em]\vspace{-2mm}
        \item Bachelor of Arts in Computer Science; Secondary in Physics. \hfill Anticipated: May 2024
        \item \textsc{Relevant coursework:} 
        \begin{itemize}[itemsep=-.5em, leftmargin=1em]\vspace{-3mm}
          \item Systems Programming (CS61), Artificial Intelligence (CS182)
                Abstraction and Design in Computation (CS51), \\
                Intro to Algorithms (CS120), 
                Applied Linear Algebra (AM120), 
                Intro to Probability (STAT110).
        \end{itemize}
        \item \textsc{Relevant school projects:} 
        \begin{itemize}[itemsep=-.4em, leftmargin=1em]\vspace{-3mm}
              \item Turing-complete \href{https://book.cs51.io/pdfs/abstraction-21-project.pdf}{OCaml interpreter},
              kernel called \href{https://cs61.seas.harvard.edu/site/2021/WeensyOS/}{WeensyOS},
              a \href{https://cs61.seas.harvard.edu/site/2021/Shell/}{Bash Shell} in C++, 
              and a Python \href{http://procaccia.info/courses/CS182-F22/pset3.pdf}{Ghost AI}.
        \end{itemize}
    \end{itemize}
  \vspace{.5mm}

  %Experience
  \noindent{\textsc{\large Experience}}\vspace{-8pt}\\
  \noindent\makebox[\linewidth]{\rule{7.5in}{0.3pt}}

    \noindent \textbf{Quantum Software Developer} \hfill May-Aug 2023\\
    \textsc{IBM Quantum}  \hfill Yorktown Heights, NY
    \begin{itemize}[itemsep=-.4em, leftmargin=1em]\vspace{-2mm}
      \item Parametric Update
      \item Qiskit Early Access completion
      \item Observability
      \item Refactoring
    \end{itemize}

    \noindent \textbf{Software Engineer} \hfill Jun-Dec 2022 \\
    \textsc{Teamcore at Harvard University} \hfill Cambridge, MA
    \begin{itemize}[itemsep=-.4em, leftmargin=1em]\vspace{-2mm}
      \item Revamped error handling for the PAWS SMART API by programming a Python interface that expedited testing requests. 
      \item Crafted 15 artificial parks in QGIS and Python to verify ML predictions. The interface would handle the artificial data with HTTP requests. Outlined the program with greater detail in the API's deployment guide.
    \end{itemize}

    \noindent \textbf{Sensors Intern} \hfill May-Aug 2022\\
    \textsc{{Wildlife Conservation Society}} \hfill Remote / NY
    \begin{itemize}[itemsep=-.4em, leftmargin=1em]\vspace{-2mm}
      \item Developed about 100 queries in SQL to then build an article processing interface with Python to deploy a virtual library.
      \item Researched and drafted an 8-page
      \href{https://bit.ly/AI-Advancing-Video-Processing-and-CTDS}{white-paper} to review state-of-the-art AI video processing and conservation tools.
    \end{itemize}
  \vspace{.5mm}
  
  % Projects
  \noindent{\textsc{\large Projects}}\vspace{-8pt}\\
  \noindent\makebox[\linewidth]{\rule{7.5in}{0.3pt}}
    \noindent \href{https://interviewinsight.com}{\textbf{AI Chat-Bot \& Web-Application}} - Co-Founder of Entrevista \hfill Apr-May 2023
    \begin{itemize}[itemsep=-.4em, leftmargin=1em]\vspace{-2mm}
      \item Developed, tested, and launched a consulting case-interview MVP with Python, React, and AWS.
      \item Presented MVP and became a Y-Combinator finalist.
    \end{itemize}
    \noindent \href{https://alejandraprj.com/pcrisite}{\textbf{Web-Scraper \& Emailer}} - Freelance Software Engineer at Pre-College Research Institute \hfill Apr-May 2023
    \begin{itemize}[itemsep=-.4em, leftmargin=1em]\vspace{-2mm}
      \item Developed a web app with React and Python to scrape contact information of Title 1 schools in the US.
      \item Automated subscription-based email lists with 3000 contacts for outreach to quialifying schools.
      \item Deployed process for organizational use and re-vamped process with automated pipelines.
    \end{itemize}
  \vspace{.5mm}

  % Activities
  \noindent{\textsc{\large Activities}}\vspace{-8pt}\\
  \noindent\makebox[\linewidth]{\rule{7.5in}{0.3pt}}
  % TEACHING FELLOW
  \noindent\textbf{Teaching Fellow} \hfill Sep-Dec 2022 \\
  \textsc{Harvard University} \hfill Cambridge, MA
  \begin{itemize}[itemsep=-.4em, leftmargin=1em]\vspace{-2mm}
    \item Facilitated a \href{https://cs61.seas.harvard.edu/site/2022/#gsc.tab=0}{Systems course} of about 200 students by holding office hours and a section of about 25 students weekly.
    \item Covered 6 topics using C++: data memory and representation, assembly, kernel, caching, shell, and synchronization.
  \end{itemize}
  % DIB ADVOCACY DIRECTOR
  \noindent\textbf{DIB Advocacy Director} \hfill Aug-Dec 2022 \\
  \textsc{Women in Computer Science} \hfill Cambridge, MA
  \begin{itemize}[itemsep=-.4em, leftmargin=1em]\vspace{-2mm}
    \item Oversaw and collaborated with 8 members on initiatives to promote diversity and inclusion and organized events to provide more resources to underrepresented groups.
  \end{itemize}
  \vspace{.5mm}

  % Skills
  \noindent{\textsc{\large Skills}}\vspace{-8pt}\\
  \noindent\makebox[\linewidth]{\rule{7.5in}{0.3pt}}
  % SKILLS SECTION
  \noindent\textbf{Programming:} Proficient (3+ years) in Python and C++. Experienced (1+ years) with Java, OCaml, and SQL.\\
  \textbf{Development:} Proficient (3+ years) in HTML/CSS. Experienced (1+ years) with PHP, JavaScript, TypeScript, and React.\\
  \textbf{Environments:} Skilled with QisKit, AWS, Docker, OpenAI, Linux, Azure, MATLAB, and x86-Assembly.\\
  \textbf{Language:} Fluent in Spanish (native), intermediate in Mandarin Chinese, and elementary in Japanese.\\

\end{document} 

