\documentclass[11pt]{article}
\usepackage[letterpaper, margin=0.5in, showframe=false]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{mathptmx}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage[super]{nth}
\renewcommand{\labelitemi}{\textbullet}
\usepackage{enumitem}
\usepackage{fontawesome}


\thispagestyle{empty}
\definecolor{myBlue}{rgb}{.2, .35, .59}
\definecolor{darkBlue}{rgb}{.094117, .2, .3529}
\hypersetup{
  colorlinks   = true,      % Color links instead of boxes
  urlcolor     = myBlue, % Color for external hyperlinks
  linkcolor    = darkBlue,  % Color of internal links
  citecolor    = red        % Color of citations
}

\begin{document}

  \centerline{\Large{Alejandra J. Perea Rojas}}\vspace{1mm}

  \centerline{
    \href{mailto:aperearojas@college.harvard.edu}{\faEnvelopeO~aperearojas@college.harvard.edu} 
    $\cdot$ \href{https://github.com/alejandraprj}{\faGithub~github.com/alejandraprj}
    $\cdot$ \href{https://alejandraprj.com}{\faGlobe~alejandraprj.com}
  }\vspace{2mm}

  % Education
  \noindent{\textsc{\large Education}}\vspace{-7pt}\\
  \noindent\makebox[\linewidth]{\rule{7.5in}{0.3pt}}

  \noindent \textbf{Harvard University} \hfill Cambridge, MA
    \begin{itemize}[itemsep=-.4em, leftmargin=1em]\vspace{-2mm}
        \item Bachelor of Arts in Computer Science; Secondary in Physics. \hfill Anticipated: May 2024
        \item Relevant coursework: Intro to Algorithms (CS120), 
                  Systems Programming (CS61), Artificial Intelligence (CS182)
                  Abstraction and Design in Computation (CS51), 
                  Applied Linear Algebra (AM120), 
                  Intro to Probability (STAT110). % TODO CS124, PHYS143, more..?
    \end{itemize}

  %Experience
  \noindent{\textsc{\large Experience}}\vspace{-7pt}\\
  \noindent\makebox[\linewidth]{\rule{7.5in}{0.3pt}}

    % PAWS
    \noindent \textbf{Software Engineer}\\
    \textsc{Harvard University} \hfill Jun-Dec 2022, Cambridge, MA
    \begin{itemize}[itemsep=-.4em, leftmargin=1em]\vspace{-2mm}
      \item Revamped error handling for the PAWS SMART API by programming a Python interface that expedited testing requests. 
      \item Crafted 15 artificial parks in QGIS and Python to verify ML predictions. The interface would handle the artificial data with HTTP requests. Outlined the program with greater detail in the API's deployment guide.
    \end{itemize}
    
    % WCS
    \noindent \textbf{Sensors Intern}\\
    \textsc{{Wildlife Conservation Society}} \hfill May-Aug 2022, Remote / NY
    \begin{itemize}[itemsep=-.4em, leftmargin=1em]\vspace{-2mm}
      \item Developed about 100 queries in SQL to then build an article processing interface with Python to deploy a virtual library.
      \item Researched and drafted an 8-page
      \href{https://bit.ly/AI-Advancing-Video-Processing-and-CTDS}{white-paper} to review state-of-the-art AI video processing and conservation tools.
    \end{itemize}

    \noindent \textbf{AI Intern}\\
    \textsc{{C Minds through DRCLAS}} \hfill Apr-Aug 2021, Remote / MX
    \begin{itemize}[itemsep=-.4em, leftmargin=1em]\vspace{-2mm}
      \item Expedited three research briefings to assist in the set-up of a Diabetic Retinopathy AI-based Screening Program in Jalisco. 
      \item Assisted in the installing of a Living Lab in Yucatan with the finalization of three AI-based conservation projects.
    \end{itemize}

  % Activities
  \noindent{\textsc{\large Activities}}\vspace{-7pt}\\
  \noindent\makebox[\linewidth]{\rule{7.5in}{0.3pt}}

  % WEB DIRECTOR OF HPC!

  % CS61
  \noindent\textbf{Systems Course Assistant}  \\
  \textsc{Harvard University} \hfill Sep-Dec 2022, Cambridge, MA
  \begin{itemize}[itemsep=-.4em, leftmargin=1em]\vspace{-2mm}
    \item Facilitated a Systems course of about 200 students by holding office hours and a section of about 25 students weekly.
    \item Covered 6 topics using C++: data memory and representation, assembly, kernel, caching, shell, and synchronization.
  \end{itemize}

  % WiCS
  \noindent\textbf{DIB Advocacy Director} \\
  \textsc{Women in Computer Science} \hfill Aug-Dec 2022, Cambridge, MA
  \begin{itemize}[itemsep=-.4em, leftmargin=1em]\vspace{-2mm}
    \item Oversaw and collaborated with 8 members on initiatives to promote diversity and inclusion and organized events to provide more resources to underrepresented groups.
  \end{itemize}

  % Projects
  \noindent{\textsc{\large Projects}}\vspace{-7pt}\\
  \noindent\makebox[\linewidth]{\rule{7.5in}{0.3pt}}
    % CS182
    \noindent \textbf{COMPSCI 182} - \href{http://procaccia.info/courses/CS182-F22/pset2.pdf}{\textsc{Sudoku Solver}} and \href{http://procaccia.info/courses/CS182-F22/pset3.pdf}{\textsc{Ghost AI}} \hfill Oct-Dec 2022
    \begin{itemize}[itemsep=-.4em, leftmargin=1em]\vspace{-2mm}
      \item Created a Sudoku Solver using forward checking and MRV heuristics as a computer satisfaction problem.
      \item Developed a Ghost AI with Minimax Agents and Alpha Beta Agents with alpha-beta pruning. 
    \end{itemize}\vspace{-1mm}
    % MiniML CS51 % it's obvious that it's turing complete
    \noindent \textbf{COMPSCI 51} - \href{https://book.cs51.io/pdfs/abstraction-21-project.pdf}{\textsc{MiniML}} \hfill May 2022
    \begin{itemize}[itemsep=-.4em, leftmargin=1em]\vspace{-2mm}
      \item Built an OCaml interpreter with various features, including unary and binary types, operators, conditionals, and higher-order and recursive functions, using the substitution and dynamic scoped environment models. 
    \end{itemize}\vspace{-1mm}
    % CS61
    \noindent \textbf{COMPSCI 61} - 
      \href{https://cs61.seas.harvard.edu/site/2021/WeensyOS/}{\textsc{Kernel}} and 
      \href{https://cs61.seas.harvard.edu/site/2021/Shell/}{\textsc{Shell}} \hfill Oct-Dec 2021
    \begin{itemize}[itemsep=-.4em, leftmargin=1em]\vspace{-2mm}
      \item Implemented a kernel, called WeensyOS, with features such as kernel isolation, process isolation, virtual page allocation, forking, shared memory, and overlapping virtual memory address spaces, as well as an exiting function.
      \item Created a Bash shell in C++ with foreground and background commands (including the cd command), command lists, conditionals, pipelines, redirections, and the interrupt signal, while handling zombie processes.
    \end{itemize}
  
  % Skills
   \noindent{\textsc{\large Skills}}\vspace{-7pt}\\
   \noindent\makebox[\linewidth]{\rule{7.5in}{0.3pt}}
   \textbf{Programming:} Proficient (3+ years) in Python and C++. Experienced (1+ years) with Go, OCaml, Java, and SQL.\\
   \textbf{Development:} Proficient (3+ years) in HTML/CSS. Experienced (1+ years) with PHP, JavaScript, TypeScript, and Flask.\\
   \textbf{Environments:} Skilled with Linux, x86 Assembly, Azure, AWS, Docker, and MATLAB.\\
   \textbf{Language:} 
     Fluent in Spanish (native), intermediate in Mandarin Chinese, and elementary in Japanese.\\
   % \noindent \textbf{Deployed:}   # React and Node.JS
   %   \href{https://alejandraprj.com}{www.alejandraprj.com},
   %   \href{https://harvardpsychedelicsclub.org}{www.harvardpsyschedelicsclub.org}\\


\end{document} 

